Using VDMS to Search 100M Images: A Piece of Cake

### 2020-01-27 yfcc100m/paper/vldb2020/eval.tex
Update eval section

We use the Yahoo! Flickr Creative Commons 100m (YFCC100M) dataset ~\cite{Thomee_2016} for a large collection of 100 million public Flickr media objects.  This dataset contains approximately 99.2 million images and 0.8 million videos along with respective metadata characterized by 25 fields such as the identifier (metaid), the user who created the media (image/video), the date the media was taken and uploaded, the location in longitude/latitude coordinates, and the device the media was captured.  The metadata also provides information including the URL to download the media, a title, a description of the media, user and machine tags, and license information.  To understand the content of the media, the YFCC100M also provides autotags which is a set of comma-separated tags and confidence scores generated from 1,570 trained Caffe binary SVM classifiers.

@@

For the experiments, we built VDMS and MySQL databases for the YFCC100M dataset sizes 100k, 500k, 1M, 5M, 10M, 50M, and 100M. The VDMS Python client library was used to add the necessary elements to the database.  In the database, we insert the nodes for the 1,570 autotags and the YFCC media objects with the appropriate metadata. To add the autotag confidence scores, we parse the autotag data and add a connection between the media object and tag nodes with metadata denoting its appropriate confidence score. Table~\ref{table:vdmsnodes} shows the number of elements in each database.

Alternatively, three tables were created for the MySQL system: taglist, metadata, and autotags.  The number of rows in the MySQL databases are shown in Table~\ref{table:mysqltables}. The taglist table contains the 1,570 autotags where each entry is given an integer key named tagid.  The metadata table contains image metadata where the metadata identifier is the primary key. The autotags table contains the confidence scores for the generated autotags for metadata entries of the metadata table.  This table also relates the other two tables and includes the tagid associated with the autotag and the metaid associated with the metadata identifier which are both keys to allow faster retrieval of data.

@@

@@

The VDMS and MySQL databases have comparable number of elements as shown in Table~\ref{table:vdmsnodes} and ~\ref{table:mysqltables} but VDMS outperforms MySQL in build speed.  Figure~\ref{fig:db_time_size} illustrates how VDMS can build databases faster than MySQL as the database size grows.  On average, it took MySQL 3.72x hours longer to build than VDMS. For example, to build the 100M database, MySQL took 263 hours while VDMS only needed 72.5 hours.  This is a difference of over a week of processing data with VDMS missing less than 0.001\% images and 0.048\% connections from the entire dataset.  Alternatively, VDMS requires more storage, shown in Figure~\ref{fig:db_time_size}, to store relationship information about each node/connection.  This may become a factor if storage is a limitation but for the YFCC databases, VDMS required 30-41\% more storage than MySQL.

@@

@@

@@

Figure~\ref{fig:q1_latency} illustrates the performance of a simple query (find metadata/images for an alligator and resize the image to 224x224) over 15 iterations. In this case, the performance of VDMS is always better than MySQL and increases as the size of the database grows.  For the 100M database, the VDMS metadata and image query times are almost \textbf{6x?} and \textbf{3x?} faster than MySQL, respectively.

@@

>>>>

The Yahoo! Flickr Creative Commons 100m (YFCC100M) dataset is a large collection of 100 million public Flickr media objects.  It contains approximately 99.2 million images and 0.8 million videos with metadata characterized by 25 fields such as the identifier, the user, the date the media was taken/uploaded, the location in longitude/latitude coordinates, and the device the media was captured.  The metadata also provides information including the URL to download the media object, a title, a description, user and auto-generated tags, and Creative Commons license information.  The YFCC100M dataset also used a deep learning approach to generate autotags data which is a set of comma-separated concepts such as people, scenery, objects, and animals and confidence scores generated from 1,570 trained Caffe classifiers ~\cite{Thomee_2016}.

@@

We built VDMS and MySQL databases using the YFCC100M dataset with incremental sample sizes 100k, 500k, 1M, 5M, 10M, 50M, and 100M. For each dataset size, we created a PMGD graph from the YFCC100m metadata, the YFCC100m autotags associated with each metadata identifier, and a list of 1,570 autotags using 100 concurrent VDMS Python clients.  With simple queries, we insert 1,570 nodes for the autotags and insert nodes for the YFCC media objects with the appropriate metadata.  Adding the autotag confidence scores is a recursive process and requires more complex queries than adding the previous nodes. For each metadata identifier in autotags, the query must find the associated metadata node and a tag node for an autotag listed for the identifier.  A connection between the two nodes is created with the confidence score as a property. The number of metadata nodes are dependent on the database size and the connections are responsible for 90\% of the elements in each database as shown in Table~\ref{table:vdmsnodes}. It is important to note that the metadata identifier, autotags, and longitude/latitude coordinates are set as indexes of the database to allow faster retrieval of the metadata.

@@

Alternatively, each MySQL database is created from the same data using three tables: taglist, metadata, and autotags.  By default, MySQL accounts for thread concurrency when processing requests but we increased the buffer pool size to handle the large amounts of data to avoid locking ~\cite{mysql}. Using a Python client and simple queries, the taglist table is read from the list of tags with an auto-incremented tagid as an index and the metadata table is read from the YFCC100m metadata using the identifier as an index. The autotags table contains the generated autotags and confidence scores for metadata entries of the metadata table. To generate the table, we split the autotags data for each database by the metadata identifier and autotag into new files. The new files are read into the respective autotags table with the metadata identifier and tagid as indexes.

@@

@@

The VDMS and MySQL databases have comparable number of elements as shown in Table~\ref{table:vdmsnodes} and ~\ref{table:mysqltables} but VDMS outperforms MySQL in build speed.  Figure~\ref{fig:db_time_size} illustrates how VDMS can build databases faster than MySQL as the database size grows.  A key difference in ingestion times is the low-level implementation of how MySQL reads data from the files and saves them to the tables versus VDMS ability to add components concurrently. In comparison, on average, it took MySQL 3.72x hours longer to build each database than VDMS. For example, to build the 100M database, MySQL took 263 hours while VDMS only needed 72.5 hours.  This is a difference of over 7 days of processing data with VDMS missing less than 0.001\% images and 0.048\% connections from the entire dataset.  Alternatively, VDMS requires more storage, shown in Figure~\ref{fig:db_time_size}, to store relationship information about each node/connection.  This may become a factor if storage is a limitation but for the YFCC databases, VDMS required 30-41\% more storage than MySQL.

@@

To evaluate the access to metadata and images, we use the following four queries:
\begin{enumerate}
\item {\bf {\em 1tag}}: Find metadata/images of alligator.
\item {\bf {\em 1tag\_resize}}: Find metadata/images of alligator and resize to 224x224.
\item {\bf {\em 1tag\_resize\_geo}}: Find metadata/images of alligator, resize to 224x224, and in a particular geolocation (20 degrees radius).
\item {\bf {\em 2tag\_resize}}: Find metadata/images of BOTH alligator and lake and resize to 224x224.
\end{enumerate}

@@

@@

An image and metadata search on the YFCC100M databases are very extensive and would benefit from multithreading to process queries simultaneously.  Figure~\ref{fig:concurrency_vdms} illustrates a concurrency analysis for the \textit{1tag} query using VDMS to investigate the number of concurrent clients to use for the per-query performance analysis.  This figure shows the metadata performance plateaus at 32 clients and the image performance at 56 clients for a simple query. To further investigate, Figure~\ref{fig:q_throughput_32} and Figure~\ref{fig:q_throughput_56} illustrate the throughput performance for the \textit{1tag} and \textit{1tag\_resize} queries for 32 and 56 clients, respectively.  On the 56-client experiment, a 10x difference occurs between VDMS and MySQL in metadata throughput while 32 clients is similar but not as high. The overall performance for both MySQL and VDMS is better with 56 clients; therefore, we used this value for our per-query analysis.
